00-datawrangling.Rmd

### 2019-03-14 scripts/00-datawrangling.Rmd
now with underscores no dash

@@

# replace dashes with peroids and make rowname, to match colnames(countData)
colData$V1 <- gsub("-", ".", colData$V1)
row.names(colData) <- colData$V1

@@

```{r write}
write.csv(colData_manipluation, "../results/colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/countData_characterization.csv", row.names = TRUE) 
```

>>>>

# replace dashes with periods (to make deseq happy)
colnames(countData) <- gsub('-', '.', colnames(countData))

@@

# replace dashes with periods and make rowname, (to make deseq happy)
colData$V1 <- gsub("-", ".", colData$V1)
row.names(colData) <- colData$V1

@@

```{r write}
write.csv(colData_manipluation, "../results/00_colData_manipluation.csv", row.names = TRUE) 
write.csv(countData_manipluation, "../results/countData_manipluation.csv", row.names = TRUE) 
write.csv(colData_characterization, "../results/00_colData_characterization.csv", row.names = TRUE) 
write.csv(countData_characterization, "../results/00-countData-characterization.csv", row.names = TRUE) 
```
